---
title: "Formative.rmd"
author: "He Zhang"
date: "10/5/2017"
output: html_document
---
```{r}
D1 <- read.csv("~/Downloads/HMXPC13_DI_v2_5-14-14.csv", heade=T)
D1
```

#5. What does the DI suffix that is appeneded to two of the variable names mean?
DI=deidentifying information

#6. How many people enrolled in HarvardX/CS50x recieved certification in 2012? 
There are 1287 students who enrolled in HarvardX/CS50x recieved certification in 2012.
```{r}
sum(D1$course_id== "HarvardX/CS50x/2012" & D1$certified==1)
```

#7. How many people registered for HarvardX/CS50x from Columbia on October 15, 2012? 
There are 10 people who registered for HarvardX/CS50x from Colombia on October 15, 2012.
```{r}
sum(D1$course_id== "HarvardX/CS50x/2012" & D1$final_cc_cname_DI=="Colombia" & D1$start_time_DI=="2012-10-15")
```

#8. Create a new data frame (D2) that includes student ID and registration date for all students from a country of your choice
```{r}
# D2 <- subset(D1, final_cc_cname_DI=='China', select=c(userid_DI,start_time_DI, final_cc_cname_DI))
D2
```

#9. Create a new data frame (D3) in which the column names are the registration dates, with one column containing the student ids and all other cells indicating a 1 if the student registered on that date or an NA if they did not.
```{r}
D3<-D1[c(2,12)]
D3$value <- 1
D3
library("tidyr")
library("dplyr")
D3=mutate(D3, row=row_number())
D3 <- spread(D3, key="start_time_DI",value="value", fill = NA, convert = FALSE, drop = TRUE)
D3
```

#10. Now make the row names of D3 the student ids on your new data frame and remove the user id column from your data frame
```{r}
names(D3)[names(D3) == 'row'] <- 'student_id'
D3 <- D3[c(-1)]
D3
```

#11. Convert your data frame to a matrix (M1)
```{r}
M1 <-as.matrix(D3)
M1
```

#12. Create a new matrix which is the transposed version of your matrix (M2)
```{r}
M2 <-t(M1)
M2
```
#13 Create a third matrix (M3) that is a student by student matrix where the cells in the matrix represent if two studentes registered on the same day.

```{r}
M3<-M1%*%M2
```


#14 Convert the diagonal of your matrix into NAs
```{r}
diag(M1)=NA
M1
```

